\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-14 papers/jss/article.Rnw
Section 5 (types): Add a sentence noting that three types in particular need special attention, to transition to the three subsections on booleans, uint32s, and int64s.
Section 6 (Converting R data structures to Protocol Buffers):
Rewrite first two sentences to make the distinction between the
previous sections describing methods for working with messages and a
specific pre-defined schema, and the function in this section
describing a universal schema that can be used on arbitrary R data
structures.  This seems like the more accurate distinction than
calling it low-level vs high-level as was d

Table~\ref{table-get-types} details the correspondence between the
field type and the type of data that is retrieved by \verb|$| and \verb|[[|
extractors.

@@

The previous sections discussed functionality in the \pkg{RProtoBuf} package
for creating, manipulating, parsing and serializing Protocol Buffer messages.
In addition to these low-level methods, the package also has some high level
functionality for automatically converting R data structures into protocol
buffers and vice versa. The \texttt{serialize\_pb} and \texttt{unserialize\_pb}
functions serialize arbitrary R objects into a universal Protocol Buffer 
message:

@@

In order to accomplish this, \pkg{RProtoBuf} uses the same catch-all \texttt{proto}
schema used by \pkg{RHIPE} for exchanging R data with Hadoop \citep{rhipe}. This 
schema, which we will refer to as \texttt{rexp.proto} is printed in appendix 
\ref{rexp.proto}. The Protocol Buffer messages generated by \pkg{RProtoBuf} and
\pkg{RHIPE} are naturally compatible between the two systems because they use the 
same schema. This shows the power of using a schema based cross-platform format such
as Protocol Buffers: interoperability is archieved without effort or close coordination.

>>>>

Table~\ref{table-get-types} details the correspondence between the
field type and the type of data that is retrieved by \verb|$| and \verb|[[|
extractors.  Three types in particular need further attention due to
specific differences in the R language.

@@

The previous sections discussed functionality in the \pkg{RProtoBuf} package
for creating, manipulating, parsing and serializing Protocol Buffer
messages of a specific pre-defined schema.  The package also provides
methods for converting arbitrary R data structures into protocol
buffers and vice versa with a universal R object schema. The \texttt{serialize\_pb} and \texttt{unserialize\_pb}
functions serialize arbitrary R objects into a universal Protocol Buffer 
message:

@@

In order to accomplish this, \pkg{RProtoBuf} uses the same catch-all \texttt{proto}
schema used by \pkg{RHIPE} for exchanging R data with Hadoop \citep{rhipe}. This 
schema, which we will refer to as \texttt{rexp.proto}, is printed in appendix 
\ref{rexp.proto}. The Protocol Buffer messages generated by \pkg{RProtoBuf} and
\pkg{RHIPE} are naturally compatible between the two systems because they use the 
same schema. This shows the power of using a schema based cross-platform format such
as Protocol Buffers: interoperability is archieved without effort or close coordination.
